\DTLgidxSetDefaultDB{glossary}

\newterm
[
   description={The traditional Filipino dance involving two bamboo sticks, where a dancer moves in and out of the rhythmically tapped sticks.},
   plural={}
]
{Tinikling}

\newterm
[
   description={An open-source computer vision library widely used for real-time image capture and processing, including camera I/O, preprocessing, filtering, and contour extraction.},
   plural={}
]
{OpenCV}

\newterm
[
   description={A class of deep neural networks that automatically learn spatial filters from image data and are widely used for visual classification tasks such as hand pose recognition.},
   plural={CNNs}
]
{CNN (Convolutional Neural Network)}

\newterm
[
   description={A commercial infrared-based hand-tracking system that uses stereo cameras and near-infrared illumination to generate dense, low-latency 3D hand data.},
   plural={}
]
{Ultraleap}

\newterm
[
   description={The computational pipeline of detecting a hand, extracting features or landmarks, and classifying the resulting input into a specific gesture with low latency and high reliability.},
   plural={}
]
{Hand Gesture Recognition}

\newterm
[
   description={A framework for building multimodal applied machine learning pipelines, including computer vision models like hand gesture recognition.},
   plural={}
]
{MediaPipe}

\newterm
[
   description={A type of recurrent neural network used for temporal modeling tasks, capable of remembering long-term dependencies in data sequences.},
   plural={}
]
{LSTM (Long Short-Term Memory)}

\newterm
[
   description={The immediate evaluation or response provided during a performance or action, especially important in learning environments.},
   plural={}
]
{Real-time feedback}

\newterm
[
   description={A computer vision technique used to detect human poses (such as hand or body positions) from images or videos, often used for gesture and movement analysis.},
   plural={}
]
{Pose estimation}

\newterm
[
   description={A technique used in machine learning to artificially increase the size of a dataset by applying transformations such as rotation, flipping, scaling, and cropping.},
   plural={}
]
{Data Augmentation}

\newterm
[
   description={The ability to run an application across multiple platforms, such as Windows, macOS, and mobile devices, without needing platform-specific code.},
   plural={}
]
{Cross-platform deployment}

\newterm
[
   description={A technique used to align time sequences by minimizing the distance between them, useful for applications like gesture recognition and speech processing.},
   plural={}
]
{Dynamic Time Warping}

\newterm
[
   description={Technology that overlays digital information (e.g., images, sounds) onto the real world to enhance or augment one's perception of the environment.},
   plural={}
]
{AR (Augmented Reality)}

\newterm
[
   description={Programmable systems or devices that interact with the physical environment (or manage devices that interact with the physical environment). These systems/devices detect or cause a direct change through the monitoring and/or control of devices, processes, and events. Examples include industrial control systems, building management systems, fire control systems, and physical access control mechanisms.},
   plural={}
]
{Operational Technologies}
